Multisensor Architecture for an Intersection Management System

### 2015-03-22 ch2-mdf_ims.tex
Started table of fusion algorithms.
Fusion algorithms section finished. Enhancement in tables. Included enumitem package.

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.4]{fig/2/WaterfallModel.png}
\caption{Waterfall model. (from \cite{Esteban2005}).}
\label{WaterfallModel}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{|c | c|}
\hline
\textbf{Category} & \textbf{Data Fusion Model} \\
\hline
\multirow{2}{*}{Abstract Model} & Waterfall Model \cite{Harris1998} \\
& Boyd Loop \cite{Boyd1987} \\
\hline
\multirow{3}{*}{Generic Architecture} & JDL Model \cite{White1991} \\
& Multisensor Fusion Integration Model \cite{Luo1989} \\
& Omnibus model \cite{Bedworth2000} \\
\hline
\multirow{3}{*}{Rigid Architecture} & LAAS Architecture \cite{Alami1998} \\
& DFuse Architecture \cite{Kumar2003} \\
& Time-triggered Model \cite{Elmenreich2001} \\
\hline
\end{tabular}
\caption{Classification of data fusion models}
\label{fusionModelsClas}
\end{table}

@@

Luo in \cite{Luo2011} propose a classification for fusion algorithms based on the level of fusion. Low-level fusion refers to the merge of raw data or signals, mid-level fusion refers to the fusion of features and High-level fusion refers to the process of fuse decisions.

Khaleghi in \cite{Khaleghi2013} describes a classification for fusion algorithms based on challenging problems that arise from the data to be fused, due to the variety of sensors and the nature of the application environment. This classification is not on the algorithms directly, but on the theory or framework in which they originate. Four types of data are enumerated: Imperfect data, correlated data, inconsistent data and disparate data. For thi

>>>>

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.4]{fig/2/WaterfallModel.png}
\caption{Waterfall model (from \cite{Esteban2005}).}
\label{WaterfallModel}
\end{figure}

@@

\begin{table}
\footnotesize
\centering
\begin{tabular}{|c | c|}
\hline
\textbf{Category} & \textbf{Data Fusion Model} \\
\hline
\multirow{2}{*}{Abstract Model} & Waterfall Model \cite{Harris1998} \\
& Boyd Loop \cite{Boyd1987} \\
\hline
\multirow{3}{*}{Generic Architecture} & JDL Model \cite{White1991} \\
& Multisensor Fusion Integration Model \cite{Luo1989} \\
& Omnibus model \cite{Bedworth2000} \\
\hline
\multirow{3}{*}{Rigid Architecture} & LAAS Architecture \cite{Alami1998} \\
& DFuse Architecture \cite{Kumar2003} \\
& Time-triggered Model \cite{Elmenreich2001} \\
\hline
\end{tabular}
\caption{Classification of data fusion models}
\label{fusionModelsClas}
\end{table}

@@

Luo in \cite{Luo2011} propose a classification for fusion algorithms based on the level of fusion. Low-level fusion refers to the merge of raw data or signals, mid-level fusion refers to the fusion of features and High-level fusion refers to the process of fuse decisions. Khaleghi in \cite{Khaleghi2013} describes a classification for fusion algorithms based on challenging problems that arise from the data to be fused, due to the variety of sensors and the nature of the application environment. This classification is not on the algorithms directly, but on the theory or framework in which they originate. Four types of data are enumerated: Imperfect data, correlated data, inconsistent data and disparate data. These two approaches of fusion algorithms classification are summarized in tables \ref{fusionAlgClasLuo} and \ref{fusionAlgClasKhaleghi}.

\begin{table}[ht!]
\footnotesize
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{\textbf{Low level fusion}} & \textbf{Medium level fusion} & \textbf{High level fusion} \\
\hline
\multicolumn{2}{|c|}{\textit{Estimation methods}} & \textit{Classification methods} & \textit{Inference methods} \\
\hline
\parbox{2.5cm}{
	Recursive:
	\begin{itemize}[leftmargin=.07in]
		\item Kalman filter
		\item Extended Kalman filter
	\end{itemize}
	Non-Recursive:
	\begin{itemize}[leftmargin=.07in]
		\item Weighted average
		\item Least squares
	\end{itemize}
	}
 & 
 \parbox{2.5cm}{	 
 	Covariance-based:
	\begin{itemize}[leftmargin=.07in]
		\item Cross covariance
		\item Covariance intersection
		\item Covariance union
	\end{itemize}
	}
&
 \parbox{3cm}{	 
	\begin{itemize}[leftmargin=.07in, noitemsep]
		\item Parametric templates
		\item Cluster analysis
		\item K-means clustering
		\item Learning vector quantization
		\item Kohonen feature map
		\item Artificial neural networks
		\item Support vector machines
	\end{itemize}
	}
&
\parbox{3cm}{	 
	\begin{itemize}[leftmargin=.07in, noitemsep]
		\item Bayesian inference
		\item Particle filters
		\item Dempster-Shafer theory
		\item Expert systems
		\item Fuzzy logic
	\end{itemize}
	} \\
\hline
\end{tabular}
\caption{Classification of fusion algorithms based on level of fusion}
\label{fusionAlgClasLuo}
\end{table}

\begin{table}[ht!]
\footnotesize
\centering
\begin{tabular}{|c|c|}
\hline
\textbf{Data Problem} & \textbf{Framework} \\
\hline
\multirow{7}{*}{Imperfection} & Probabilistic \\
& Evidential \\
& Fuzzy reasoning \\
& Possibilistic \\
& Rough set theoretic \\
& HYbridization \\
& Random set theoretic \\
\hline
\multirow{2}{*}{Correlation} & Correlation elimination \\
& Correlation presence \\
\hline
\multirow{6}{*}{Inconsistency} & Sensor validation \\
& Stochastic sensor modeling\\
& Prediction \\
& Augmented state framework \\
& Combination rules \\
& Dempsters' rule \\
\hline
\multirow{3}{*}{Disparateness} & Dempster-Shafer theoretic framework \\
& Human-centered data fusion \\
& Hard-soft data fusion \\
\hline
\end{tabular}
\caption{Classification of fusion algorithms based on challeging problems in data}
\label{fusionAlgClasKhaleghi}
\end{table}
